VerticalCreekHeight

### 2022-01-14 docs/CreekDistancesRmd.Rmd

```{r}
DTM <- 
```

@@

```{r}
CreekVerticalHeight <- DistancesCrique$distvert
```

```{r}
plot(CreekVerticalHeight,  breaks=c(0,2), col='red') # les jolis bas-fonds !
```

>>>>

```{r}
data("PlotMask")

DATA_paracou_path <- paste0(Sys.getenv('DATAPATH'), "/GIS/Paracou/")

DTM <- paste0(DATA_paracou_path,"Dem.sgrd")
```

@@

```{r}
  DistancesCrique$distvert <- mask(DistancesCrique$distvert, PlotMask)
  DistancesCrique$distvert <- crop(DistancesCrique$distvert, PlotMask)

  DistancesCrique$disthorz <- mask(DistancesCrique$disthorz, PlotMask)
  DistancesCrique$disthorz <- crop(DistancesCrique$disthorz, PlotMask)

CreekDistances <- list(distvert = DistancesCrique$distvert,distHorz = DistancesCrique$disthorz)

```{r}
plot(CreekDistances$distvert,  breaks=c(0,2), col='red')

plot(CreekDistances$distHorz,  breaks=c(0,30), col='red')
```
